---
title: "Canada Marriage Lincese issue"
subtitle: "My subtitle if needed"
author: 
  - Ruiying Li
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

```


# Introduction

This paper shows the marriage lincense inssued in Canada from 2011 to 2025. we use We use @talia, @opendatatorotno, and @rohan and @sec-data as our dataset, using R programming to write code and @tidyverse to clean and test data, with ggplot to form graph, finding the trend of Marriage issue through years

# Data {#sec-data}


# Data {#sec-mydatasection}

Some of our data is of penguins (@fig-marriage), from @palmerpenguins.

```{r}
#| label: fig-marriage
#| fig-cap: Marriage license issue
#| echo: false

data |> 
  ggplot(aes(x = date, y = marriage_licenses)) +
  geom_point()

```

Talk more about it.
through the graph we found out that the marriage lincense inssue in Cnanada is increasing through years.


# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


# Additional data details



\newpage


# References